Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-25 paper/paper.tex
redid imaging system engineering a bit

We had sketched plans for an electronics system built entirely on a Linux-based flight computer as early as July 2009, but planned on using a more standard microcontroller-based autopilot system with an auxillary Linux-based computer for the imaging system until December 2009. After burning out our microcontroller based autopilot for the second time, we were faced with a long lead time for an expensive replacement part. On that impetus, we redesigned our electronics systems to eliminate the microcontroller autopilot and ensure all of our replacment parts would be inexpensive and commercially available from many vendors. The move to a single Linux-based flight computer, while not without obstacles, was a successful design decision, as we'll describe in this paper.

@@

We felt the Paparazzi system was full featured and proven, but we weren't satisified with the capabilities of the existing Paparazzi hardware. The ``Tiny'' v2.1\cite{paparazzi_tinyv21}, the latest autopilot hardware released by the Paparazzi project, is based on a 64 pin ARM microcontroller. Almost all of its input-output capabilities are dedicated to autopilot functions, making it difficult to expand functionality and share information (for instance, position and orientation estimates) with payload components. As previously stated, the Tiny is expensive, fragile\footnote{In our own admittedly clumsy experience} and often subject to long lead times.

@@

We elected to take many steps in the software engineering to help ensure our flight computer will operate reliably. The most important of these was code review and incremental testing. Both Pat Hickey and Bradley Lord became intimately familiar with the source code and control flow inside the autopilot software, and all patches were reviewed and tested by both engineers. Numerous other safety measures will be described in Section \ref{sec:autopilot_software}.

Because our entry is essentially an experimental system, and will always be operated with a safety pilot present, we engineered the safety pilot override to operate independently from the flight computer. We have ensured that, short of losing power to the radio control receiver and servos, the safety pilot will always be able to take over with the flick of a single switch on his radio control transmitter. We have also ensured that the flight computer's servo controller will be able to detect a loss of computer control and servos to a recoverable default. Along with careful preflight testing, careful observation, and definitive analysis of any errors encountered during flight, these measures meet the spirit and letter of competition rules.

@@

When designing the imaging system our major goals were to have 1) a camera with XXX range of motion.  2) real-time video feed from the plane.  3) ability to control the camera in real-time and take pictures.  4) ability to download pictures while in flight.  For the camera we chose the Sony Bloggie \cite{bloggie} because it was small, light, cheap, and took high resolution images and video.  In addition it came with a built in rotating lens, which simplified the construcion of the pan-tilt unit, and it can also be controlled remotely over usb, so it interfaced with our flight linux computer.  To communicate with the plane we developed custom ground station software to meet our needs and installed two sets of radios, one for the video feed, and another for communicating with the plane and downloading images.  These radios are independent from the set of radios used for the autopilot because we didn't want to have dependencies between the two systems.

>>>>

We had sketched plans for an electronics system built entirely on a Linux-based flight computer as early as July 2009, but planned on using a more standard microcontroller-based autopilot system with an auxiliary Linux-based computer for the imaging system until December 2009. After burning out our microcontroller based autopilot for the second time, we were faced with a long lead time for an expensive replacement part. On that impetus, we redesigned our electronics systems to eliminate the microcontroller autopilot and ensure all of our replacement parts would be inexpensive and commercially available from many vendors. The move to a single Linux-based flight computer, while not without obstacles, was a successful design decision, as we'll describe in this paper.

@@

We felt the Paparazzi system was full featured and proven, but we weren't satisfied with the capabilities of the existing Paparazzi hardware. The ``Tiny'' v2.1\cite{paparazzi_tinyv21}, the latest autopilot hardware released by the Paparazzi project, is based on a 64 pin ARM microcontroller. Almost all of its input-output capabilities are dedicated to autopilot functions, making it difficult to expand functionality and share information (for instance, position and orientation estimates) with payload components. As previously stated, the Tiny is expensive, fragile\footnote{In our own admittedly clumsy experience} and often subject to long lead times.

@@

We elected to take many steps in the software engineering to help ensure our flight computer will operate reliably. The most important of these was code review and incremental testing. Both Pat Hickey and Bradley Lord became intimately familiar with the source code and control flow inside the autopilot software, and all patches were reviewed and tested by both engineers. Numerous other safety measures are described in Section \ref{sec:autopilot_software}.

Because our entry is essentially an experimental system and will always be operated with a safety pilot present, we engineered the safety pilot override to operate independently from the flight computer. We have ensured that, short of losing power to the radio control receiver and servos, the safety pilot will always be able to take over with the flick of a single switch on his radio control transmitter. We have also ensured that the flight computer's servo controller will be able to detect a loss of computer control and servos to a recoverable default. Along with careful preflight testing, careful observation, and definitive analysis of any errors encountered during flight, these measures meet the spirit and letter of competition rules.

@@

When designing the imaging system our major goals were to have 
1) a camera able to capture imagery ``up to \degrees{60} in all directions from vertically below the aircraft''\cite{competition_rules}, as per the rules; 
2) a real-time video feed;
4) the ability to download pictures while in flight; and
3) the ability to remotely control the camera, particularly to trigger pictures.

It was difficult to find a camera to base our imaging system on which met all of these requirements. Many still cameras can be fitted on a pan tilt system to requirement 1, and provide a real-time ``viewfinder'' video feed to meet requirement 2. Requirement 3 could typically be managed by attaching the camera to a single board computer by USB cable, though usually the camera powers down when attached to the computer, and some sort of switch is needed to deactivate the USB cable once the data transfer is complete.

Requirement 4 had the greatest effect on our design decision. Typically, only high-end SLR-type still cameras provide a socket for remote control. These are beyond our price range, and are much larger and heavier than we would like.
We built a prototype using a Canon Powershot S5 IS \cite{powershotS5}, a camera which has no electrical remote control input, by soldering wires to the push-button pads for the shutter and zoom buttons. Those wires were attached to isolating transistors, and a microcontroller was used to control the buttons remotely But after some time, this clever circumvention burned out the whole camera, and we abandoned the scheme.
